Reconciler: A Workflow for Writing Reproducible Computational Research Papers

### 2020-07-26 ms.tex
fix pip in Dockerfile and url link in ms.tex

We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-certifying-computational-research-reproducibility}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.

>>>>

We provide an implementation\footnote{\url{https://github.com/pbizopoulos/reconciler-a-workflow-for-writing-reproducible-computational-research-papers}} of the Reconciler, that certifies the reproducibility of the arXiv version of this paper\footnote{\url{https://arxiv.org/abs/2005.12660}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages such as R~\cite{ihaka1996r} and Julia~\cite{bezanson2017julia} can be used.
